\textbf{Computational Fuzzy Extractors}

### 2013-03-18 trunk/CompFuzzExt.tex
Revising theorem 5.3

The dist-$\LWE_{n, m, q, W}$ with symbol fixing sources is implied by standard $\distLWE_{n, m, q, \chi}$~(proof in \secref{sec:proof of block theorem}).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m = \poly(n)$, let $\alpha < q$ and $\beta = \omega(1)$.  Let $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha + \beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}
\bnote{We should add some exposition here.  Some intuition about the proof.}

@@

It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
\end{enumerate}
\begin{figure}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}

@@

\label{cl:randomMatrixDist}
The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix.
In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.  Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.  Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.  Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5. For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number. Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors. Therefore, the entire matrix $\vA$ is a truly random matrix.  This completes the claim.
If $\D'$ is provided with input distributed as $\vA', \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i} = b_{m+i}^*$ is uniformly generated otherwise and  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
Then define $\vx$ as:
x_i = \begin{cases}
x_i', & \text{if }1\leq i\leq n \\
b_{m+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
\end{cases}
We denote by $\vA^*$ the matrix before step~\ref{step:randomization}.  The vector $\vx$ is uniformly random and $\vb^* = \vA^*\vx + \ve$~(where $\ve$ is $\ve'$ with $\alpha$ 0s appended).  Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
For a matrix $\vA$ we will denote the $i$-th row by $\va_i$.  We now show that for all rows $i$, if $b_i^* = \va^*_i \vx+e_i$  then $b_i = \va_i \vx + e_i$.
We have the following for all rows $i$:
\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i
%\vA_i \vx + e_i &= \sum_{j=1}^{n+\alpha} A_{ij} x_j +e_i = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}x_j)+e_i\\
%& = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j)+e_i +\sum_{k=1}^\alpha \gamma_{i, k} \sum_{j=1}^{n+\alpha} (A^*_{(m+k)j}x_j)\\
%& = b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k} = (\va_i^* \vx + e_i) + \sum_{k=1}^\alpha\gamma_{i, k} (\va_{m+k}^* \vx + e_i)\\
%& = b_i \label{reductionEq}
\label{clm:random b}
If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.
Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.  After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:
b_i = b_i^* + \sum_{k=1}^\alpha \gamma_i b_{m+k}^*.
%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each

>>>>

The $\distLWE$ with symbol fixing sources is implied by standard $\distLWE$~(proof in \secref{sec:proof of block theorem}).
%\vspace{.1in}
\begin{theorem}
\label{thm:blockLWE}
Let $n$ be a security parameter and define $q, m = \poly(n)$.  Let $\alpha< q$, $\beta  = \omega(1)$, and $W$ be a $m$-symbol fixing source over $\{0,1\}^{(m+\alpha)b}$ where $\Hoo(W) \geq mb$.  Then the $\distLWE_{n, m,q, W}$ assumption implies the $\distLWE_{n+\alpha+\beta, m+\alpha, q, W}$ w/ symbol fixing sources problem.
\end{theorem}
\bnote{We should add some exposition here.  Some intuition about the proof.}

@@

It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
\end{enumerate}
\begin{figure}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.

@@

\begin{claim}
\label{cl:randomMatrixDist}
The matrix $\vA$ generated after Step \ref{step:randomization} is a random matrix.
\end{claim}
\begin{proof}
In the randomized matrix $\vect{A}$, for $1\le i \le m$ and $n+1\le j \le n+\alpha$, $A_{ij}$ is assigned the value $\gamma_{i,(j - n)}$, which is a random value.  Similarly, for $m+1\le i \le m+\alpha$ and $n+1\le j \le n+\alpha$, each entry $A_{ij}$ is random due to the original construction of the matrix $\vA^*$.  Then before step \ref{step:randomization} the matrices $\vA', \vect{R}$ are random submatrices.  Thus, it remains to show that $\vA', \vect{R}$ remain random after step 5. For $1\le i \le m+\alpha$ and $1\le j \le n$, by construction $A_{ij} = A_{ij}'+\sum_{k=1}^\alpha \gamma_{i, k} R_{kj}$, which is a truly random number. Overall, each row vector $\va_{i}$ in $\vA$ is the sum of a random vector and a random linear combination independent vectors. Therefore, the entire matrix $\vA$ is a truly random matrix.  This completes the claim.
\end{proof}
\begin{claim}
\label{cl:random ax+e}
If $\D'$ is provided with input distributed as $\vA', \vA'\vx'+\ve'$ then $\vb = \vA \vx+\ve$ where $x_i = x_i'$ for $1\leq i \leq n$ and $x_{n+i} = b_{m+i}^*$ is uniformly generated otherwise and  $e_i = e_i'$ for $1\leq i\leq m$ and $e_i = 0$ for $m<i\leq m+\alpha$.
\end{claim}
\begin{proof}
Before step \ref{step:randomization} the claim is satisfied.  Denote by $\vx'$ the value such that $\vA'\vx'+\ve = \vb$.  
Then define $\vx^*$ as:
\[
x^*_i = \begin{cases}
x_i', & \text{if }1\leq i\leq n \\
b_{m-n+i}^*-\sum_{j=1}^n R_{i, j} x_j', & n+1\leq i\leq n+\alpha\,.
\end{cases}
\]
Then $\vx^*$ is uniformly random and $\vb^* = \vA^*\vx^* + \ve^*$~(where $\ve^*$ is $\ve'$ with $\alpha$ 0s appended).  Thus, it remains to show that step~\ref{step:randomization} preserves a solution.
%For convenience, denote by $\vx^*$ the vector where $x_i^* = x_i'$ for $1\leq i \leq n$ and $x_{n+i}^* = b_{m+i}^*$ otherwise.  
For a matrix $\vA$ we will denote the $i$-th row by $\va_i$~(similarly for the matrix formed by $\gamma_{i,j}$).  Thus it suffices to show for all rows $i$, if $b_i^* = \va^*_i \vx^*+e^*_i$  then $b_i = \va_i \vx^* + e^*_i$.
%, we have added $\alpha$ equations as well as $\alpha$ unknowns, furthermore, those $\alpha$ equations have no error.  The number of unknowns we added are $x_{n+i} = b^*_{m+i} - \sum^{n}_{j=1}R_{ij}x_j$ for $i=n+1,..., n+\alpha$.
\bnote{We need to justify these steps better.}
\bnote{Is it really standard to go to lower case for the rows?}
\xnote{lower case for vectors, which is row vector in the matrix}

\xnote{Needs to be clean up the $\gamma$, it's not correct, at least not consistent with the randomized algorithm.}
We have the following for all $i=1,..., m+\alpha$:
\begin{align*}
\va_i \vx + e_i &= \sum_{j=1}^{n+\alpha} \vA_{ij} x_j + e_i\\
& = \sum_{j=1}^{n+\alpha}\left(\left(\vA^*_{ij}+\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}\right)x_j\right) + e_i\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{j=1}^{n+\alpha}\sum_{k=1}^\alpha \gamma_{i, k} \vA^*_{(m+k)j}x_j \\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha  \gamma_{i, k} \sum_{j=1}^{n+\alpha} \vA^*_{(m+k)j}x_j\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha \gamma_{i, k} \left(\left( \sum_{j=1}^n \vR_{i, j}x_j^* \right) + x_{n+k}^*\right)\\
& = \sum_{j=1}^{n+\alpha}\vA^*_{ij}x_j + e_i + \sum_{k=1}^\alpha\gamma_{i, k} b_{m+k}^*\\
&= b_i^* +\sum_{k=1}^\alpha\gamma_{i,k} b_{m+k}^*= b_i
\end{align*}
%\begin{align*}
%\vA_i \vx + e_i &= \sum_{j=1}^{n+\alpha} A_{ij} x_j +e_i = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j+\sum_{k=1}^\alpha \gamma_{i, k} A^*_{(m+k)j}x_j)+e_i\\
%& = \sum_{j=1}^{n+\alpha}(A^*_{ij}x_j)+e_i +\sum_{k=1}^\alpha \gamma_{i, k} \sum_{j=1}^{n+\alpha} (A^*_{(m+k)j}x_j)\\
%& = b^*_i +  \sum_{k=1}^\alpha\gamma_{i, k} b^*_{m+k} = (\va_i^* \vx + e_i) + \sum_{k=1}^\alpha\gamma_{i, k} (\va_{m+k}^* \vx + e_i)\\
%& = b_i \label{reductionEq}
%\end{align*}
\end{proof}
\begin{claim} 
\label{clm:random b}
If $\D'$ is provided with the input distributed as $\vA', \vb'$ where $\vb'$ is uniformly random, then $\vb$ is uniformly random conditioned on $\vA$.
\end{claim}
\begin{proof}
Before step~\ref{step:randomization}, each $b_i^*$ is uniformly and independently random.  After step~\ref{step:randomization}, since the $b_i*$ and $\gamma_i$ are random, then each $b_i$ is a fresh random linear combination of random values:
\[
b_i = b_i^* + \sum_{k=1}^\alpha \gamma_i b_{m+k}^*.
\]
%We also need to show that $\vb$ is uniformly distributed even conditioned on $\vA$. Step~\ref{step:randomization} randomized each
